SPEI_longterm

### 2018-02-16 analysis/drought/explore_spei_longterm.Rmd
computation drought

>>>>

# Datos sequia antes y despues
* Ver los valores de spei antes y despues

```{r}

dys <- sev12 %>% filter(d_duration > 2) %>% as.data.frame() 
dys <- dys[,'maxyear']

f <- c()

for (y in dys){

  aux <- speidf %>% 
    dplyr::select(year, month, SPEI12_mean)

  aux1 <- aux %>% 
    filter(year == y + 1) %>% 
    summarise(speiyear_mean = mean(SPEI12_mean), 
              speiyear_sum = sum(SPEI12_mean)) %>% 
    mutate(droughtyear = y, t = 1)

    aux2 <- aux %>% 
    filter(year == y + 2) %>% 
    summarise(speiyear_mean = mean(SPEI12_mean), 
              speiyear_sum = sum(SPEI12_mean)) %>% 
    mutate(droughtyear = y, t = 2)

      aux3 <- aux %>% 
    filter(year == y + 3) %>% 
    summarise(speiyear_mean = mean(SPEI12_mean), 
              speiyear_sum = sum(SPEI12_mean)) %>% 
    mutate(droughtyear = y, t = 3)

  f <- rbind(f, aux1)

  }

f <- speidf %>% filter(year

  sev12

```
